\chapter{\HS License}

\section{Terms}
\begin{itemize}
	\item \textit{Software:} Helioscan, a control and analysis software for microscopes.
	\item \textit{Owner:} Brain Research Institute of University of Zurich (Winterthurerstrasse 190, 8057 Zurich, Switzerland).
	\item \textit{Licensee:} Any person who downloads, uses or stores copies of the Software.
\end{itemize}

\section{Conditions}
\begin{enumerate}
	\item The Owner hereby grants to the Licensee a revocable, nonexclusive, nontransferable, royalty-free permission to use the Software and to create and use Derivative Works subject to the terms and conditions of this license (a "Derivative Work" is a work that is a modification of, enhancement to, derived from, or based upon the Software).
	\item The permission is limited to noncommercial use unless a special agreement with the Owner is established. Noncommercial use relates only to educational, research, personal or evaluation purposes. Any other use is commercial use.
	\item The Licensee shall not grant sublicenses or otherwise distribute the Software or Derivative Products to third parties.
	\item Any source code file shall include a list of all its authors. Reducing author lists of a file is not permitted.
	\item \textbf{In any publication of scientific results based in part on use of the Software, the Licensee will cite the following publication:}

 Langer D., van't Hoff M., Keller A.J., Nagaraja C., Pfäffli O.A., Göldi M., Kasper H. and Helmchen F. HelioScan (2013): A software framework for controlling in vivo microscopy setups with high hardware flexibility, functional diversity and extendibility. \textit{J. Neurosci. Methods}, doi: 10.1016/j.jneumeth.2013.02.006. 
	\item This license can be revoked or changed by the Owner at any time. The Licensee is responsible to stay informed about the most up-to-date license conditions as published on the website with the URL \url{http://www.helioscan.org}.
	\item Any obligations that by their nature continue after the termination of this license shall remain binding upon the parties.
	\item THE OWNER DISCLAIMS ANY AND ALL PROMISES, REPRESENTATIONS, AND WARRANTIES, EXCEPT AS EXPRESSLY SET FORTH IN THIS AGREEMENT, WITH RESPECT TO ANY DATA, SOFTWARE, INFORMATION, OR OTHER MATERIAL FURNISHED TO THE LICENSEE HEREUNDER, INCLUDING THEIR CONDITION; CONFORMITY TO ANY REPRESENTATION OR DESCRIPTION; THE EXISTENCE OF ANY LATENT OR PATENT DEFECTS; AND TITLE, MERCHANTABILITY, OR FITNESS FOR A PARTICULAR PURPOSE OR USE.
	\item In no event shall the Owner be liable to the Licensee for any loss of profits; any incidental, special, exemplary, or consequential damages; or any claims or demands brought against the Owner, even if the Owner has been advised of the possibility of such damages.
	\item All remedies available to either party for one or more breaches by the other party shall be cumulative and may be exercised separately or concurrently without waiver of any other remedies. The failure of either party to act on a breach of this Agreement by the other party shall not be deemed a waiver of said breach or a waiver of future breaches, unless such waiver is in writing and is signed by the party against whom enforcement is sought.
	\item This license constitutes the entire agreement of the parties hereto and supersedes all prior representations, proposals, discussions, and communications, whether oral or in writing.
	\item This license shall be governed by the laws of Switzerland, the exclusive place of jurisdiction being \textbf{Zurich} (Switzerland).
\end{enumerate}